\name: Combining Bottom-up and top-down approaches through graph learning over interaction networks for drug-target-interaction prediction

### 2021-02-08 paper/main.tex
microAUC

\begin{figure}[!tpb]%figure1

@@

\subsection{Comparison}

@@

\section{Findings}

@@

\subsection{How to insult other methods}
\begin{itemize}
	\item Only few other methods perform their split over proteins \citep{Survey2018}, DTI-CDF does it
	\item Running split over proteins is harder than, drug and drug protein pair split (see below table)
	\item this applies for both DTI prediction and drug target affinity prediction (and Saras gene-disease association)
	\item using indications is like cheating, as not applicable for searching new drugs
	\item drug indications are highly predictive for downstream tasks, but lack capability to differentiate highly related[!tpb] drugs/proteins
	\item Stratified Cross validation is suitable for training, but \textbf{NOT} for validating and testing (Uselessly high AUPRC)
	\item microAUC is a superior and more intuitive metric for drug repurposing $\rightarrow$ why for each protein and not for each drug

>>>>

We find that...\todo[inline]{summarize key findings from Table.}

\todo[inline]{Replace/merge table:}
\begin{figure}[!tpb]%figure1

@@

@@

%\section{Findings}

@@

\subsection{How to insult other methods}
\begin{itemize}
	\item Only few other methods perform their split over proteins \citep{Survey2018}, DTI-CDF does it
	\item Running split over proteins is harder than, drug and drug protein pair split (see below table)
	\item this applies for both DTI prediction and drug target affinity prediction (and Saras gene-disease association)
	\item using indications is like cheating, as not applicable for searching new drugs
	\item drug indications are highly predictive for downstream tasks, but lack capability to differentiate highly related drugs/proteins
	\item Stratified Cross validation is suitable for training, but \textbf{NOT} for validating and testing (Uselessly high AUPRC)
	\item microAUC is a superior and more intuitive metric for drug repurposing $\rightarrow$ why for each protein and not for each drug
